Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex

>>>>

\subsubsection{Classical Planners}

A planner tries to find a sequence of actions such that a goal or maximum
reward is achieved. A classical planning problem consists out of states,
actions, conditions and a goal state.

\subsubsection{Probabilistic Planning} Classical Planners expect a
deterministic world. For many Real World applications actions happen with a
certain probability. This kind of Probabilistic Planning Problems can be
described with Markov Decision Processes (MDPs). For the purpose of our
analysis we define the problem as:

\begin{itemize}
	\item finite set of states $S$
	\item an initial state $s_o \in S$
	\item a $G \subseteq S$ of (absorbing) goal states
	\item a set $O$ of outcomes; probability of $o \in O$ is $\Pr(o)$
	\item a (total) deterministic transition function $T(o,s) \in S$ for all
		outcomes $o \in O$ and states $s \in S$
	\item sets $A(s)$ of applicable actions for each $s \in S$, together with
		function $out(a) \subseteq O$ mapping each action to a set of outcomes
		such that each outcome $o \in O$ belongs exactly to one action $act(o)$
		and $\sum_{o \in out(a)} \Pr(o) = 1$ for all $a$
\end{itemize}

% depends if we should include this, what we tell about Gourmand / RDDL...

Besides a single or multiple goals, some planning problems also include a
reward function: For every $s \in S$, $s' \in S$, and $a \in A(s)$,
$R(s,a,s')$ is the reward function. The goal if the problem is to maximize
the reward until a goal is reached. If a Finite Horizon (number of steps of the
plan) is used, the goal of the problem is to achieve the highest reward within
the horizon.

A probabilistic planner takes the probabilistic planning problem as input and
builds and outputs a plan for the problem.

In this paper we use Gourmand as a representative probabilistic planner, as
it's the improved version of Glutton, the runner-up of the IPPC-11 competition.

\subsubsection{Replanning}

An Replanning Planner takes a probabilistic problem and tries to solve it with
replanning. First the problem is determinized, a compilation from a
probabilistic problem to a deterministic problem. This deterministic problem
be solved by a classical planner which returns a plan. The Replanner then
executes the plan. If it ends up in a state which is different from the plan,
it executes the classical planner to get a new plan. This is repeated until a
goal is reached.

In this paper we use FF-Replan as a representative replanning planner.
